---
title: "Model output"
output: pdf_document
---


```{r initialise, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.align='center', warning=FALSE, message=FALSE)
library(ggplot2)
library(bayesplot)
model <- readRDS('model.rds')
data <- readRDS('data.rds')
```

The raw data, showing the set of observations recorded by each agent.
There are `r data$N_POINTS` points, with observations being made by
`r data$N_AGENTS` agents, with a total of `r data$N_CLAIMS` claims.
```{r data, out.height="450pt", out.width="850pt"}
 ggplot(as.data.frame(data[c('POINT', 'OBSERVATION', 'AGENT')]), 
    aes(x=POINT, y=OBSERVATION, colour=factor(AGENT))) + 
    geom_point() + 
    facet_wrap(~AGENT, ncol=5)
```

Comparison between the posterior distribution of the agent bias, and the 
agent bias that was used to generate the data (red)
```{r agents, out.height="450pt", out.width="450pt"}
mcmc_intervals(as.matrix(model), regex_pars=c('^agent.*')) + 
    geom_point(data=data.frame(i=seq(data$N_AGENTS, 1), 
        x=data$agent), 
        color='red', 
        alpha=0.5, 
        size=4, 
        aes(x=x, y=i))

```

Comparison between the posterior distribution of the value at each point, and 
the value of the point that was used to generate the data (red)
```{r points, out.height="450pt", out.width="450pt"}
mcmc_intervals(as.matrix(model), regex_pars=c('^point.*')) + 
    geom_point(data=data.frame(i=seq(data$N_POINTS, 1), x=data$point), 
        color='red', 
        alpha=0.5, 
        size=4, 
        aes(x=x, y=i))
```
